Pillar 1 - Sequential Pattern Mining

### 2019-03-13 Pillar 1 - Sequential Pattern Mining.Rmd
compute course_all, etc from d_transcript_augmented to exclude uninformative courses

```{r constants}
# Some old courses are present
course_all  <- unique(d_transcript$`Course ID` )
student_all <- unique(d_transcript$`Student ID`)
n_students  <- length(student_all)
```

@@

>>>>

@@

```{r constants}
course_all  <- unique(d_transcript_augmented$`Course ID` )
student_all <- unique(d_transcript_augmented$`Student ID`)
n_students  <- length(student_all)
```
